\section{Introduction}
The Internet is a web of thousands of interconnected networks, called
Autonomous Systems (AS). ASes are collections of routers with a coherent
routing policy controlled by a single administrative entity or domain
(such as an Internet service provider, a university, or a large company)
and represent connected groups of blocks of IP addresses, called IP
prefixes. These IP address aggregations determine the common path to
each contained IP address within the different networks.

ASes use the Border Gateway Protocol (BGP) to establish connections
between each other. With BGP update messages an AS can announce changes
in the local database, advertise its IP prefix to neighboring ASes, and
notify them of new ``best'' (e.g. shortest) routes to other ASes on the
Internet. These updates are also used to withdraw old paths.

\section{Analyzing BGP Traffic}
There are different projects that gather BGP data from locations around
the world since 1997 and make it publicly available along with several
tools to monitor this data in almost real-time, analyze the historic
development, or academic research. One of these tools is BGPStream, an
open-source framework with C/C++ and Python APIs. BGPStream gathers BGP
routing information some operators make publicly available from their
routers such as University of Oregon's RouteViews and RIPE RIS.

\subsection{Prefix Hijacking}
Since BGP was developed without security concerns, any AS can also claim
to own someone else’s IP prefix and thereby create invalid routes,
either by misconfiguration or attacks. This can lead to hijacked traffic
that is redirected to a wrong AS and causes outages this way, but also
to maybe even more serious security concerns. It is conceivable that the
attacker successfully masquerades as the real prefix owner or forwards
the hijacked traffic to the true destination while capturing all the
transmitted data without letting the victims know their traffic was
diverted.

\subsection{Origin Validation}
To validate the prefix origin and secure the routing infrastructure from
hijacking, a Resource Certification (RPKI) was developed on top of open
standards from the Internet Engineering Task Force (IETF) for a
validation of AS numbers and their IP prefixes against a trust anchor.
The holder of an address space can authorize ASes to rightfully
originate prefixes from this space so that the prefix of each BGP update
can be verified for origin validity before it is added to the route
decision process (e.g. rejection).

The RTRlib is an implementation of the RPKI protocol. Together with an
RPKI cache server it can be used to validate the ownership of IP
prefixes with AS numbers.

\section{Implementation}
For better modularity and interchangeability the developed application
is divided into independent back end and front end components connected
by a Unix-like pipeline.

\subsection{Back End}
The back end is the main part. It uses BGPStream to fetch the BGP data
from the RouteView project as well as additional RIPE collectors that
can be specified as parameters.

Each record of the Routing Information Base (RIB) and BGP update is then
passed to RTRlib for verification. Since a RIB file contains information
about the complete network topology relevant to the router, first the
most recent RIB file is analyzed as a single file in the Multi-Threaded
Routing Toolkit (MRT) format (if collector specified), then BGPStream's
data interface is switched to broker mode to process all updates
announced since the creation of the RIB file and to continue with
real-time processing after this. RIB and update dumps are generated
every 8 hours and 5 minutes, respectively.

Additionally, for future functionality each prefix is converted to an IP
address in host byte order and saved bitwise indexed in a binary tree
with the mask length and the AS it was announced by. This is currently
available for IPv4 addresses only. It's cogitable to implement functions
that could lookup if certain prefixes were already processed and check
if they were advertised by the same or a different AS.

\subsection{Front End}
The front end is written with ncurses for a text-based UI. It counts the
processed updates, displays the time of the last update received, and
draws a histogram with valid updates on a percentage basis for each
5-minute interval. In the bottom screen area the UI also shows a table
with the top 5 AS that produced the most invalid prefix announcements
since first RIB file or update dump read. For this table a file
maintained by Geoff Huston, Chief Scientist at the Asia Pacific Network
Information Centre (APNIC), that maps each AS number to a more
meaningful AS name, is retrieved via cURL.

Figure~\ref{fig:output} shows a sample output approximately 90 minutes
after the program was started. Since the front end should be replaced
with another version, this behaves more like a demo than a real UI.

\begin{figure}
\scriptsize
\begin{Verbatim}[frame=single]
 Processed updates:                             Last update (est.):      
            3921123                             Mon Jul  3 13:15:00 2017 
                                                                         
                                                                         
         ^                                                               
         |                                                               
 % valid |      19 19 18                                                 
 updates |17 16 ** ** ** 17 17 16 16 16 16 16 16 16                      
         |** ** ** ** ** ** ** ** ** ** ** ** ** ** 15 15 15             
         |** ** ** ** ** ** ** ** ** ** ** ** ** ** ** ** **             
         |** ** ** ** ** ** ** ** ** ** ** ** ** ** ** ** **             
         |** ** ** ** ** ** ** ** ** ** ** ** ** ** ** ** **             
         |** ** ** ** ** ** ** ** ** ** ** ** ** ** ** ** **             
         |** ** ** ** ** ** ** ** ** ** ** ** ** ** ** ** **             
         |** ** ** ** ** ** ** ** ** ** ** ** ** ** ** ** **             
         |** ** ** ** ** ** ** ** ** ** ** ** ** ** ** ** **             
         |=====|=====|=====|=====|=====|=====|=====|=====|=====>         
              10    20    30    40    50    60    70    80    time (min) 
                                                                         
                                                                         
 | Rank |            AS name            | Σ inv. upd | % of total inv. | 
 |    1 | EARTHLINK-AS, IQ              |      10300 |  31 | ***       | 
 |    2 | CAMNET-AS Telecom Cambodia, K |       3164 |   9 |           | 
 |    3 | EVOWISE, RO                   |       2308 |   7 |           | 
 |    4 | CDS-AS, UA                    |       2108 |   6 |           | 
 |    5 | MOBILINK-AS-PK PMCL /LDI IP T |       1615 |   4 |           | 
\end{Verbatim}
\caption{A sample output of the ncurses front end.}
\label{fig:output}
\end{figure}

\section{Results}
The application can be used to gather different statistical data, e.g.
the proportion of valid updates in the bar chart. As seen in
figure~\ref{fig:output}, the rate there is already above 15 percent.
However, the share depends on the specific time range. Also the rates
are typically lower with RIB files. Table~\ref{tab:rrc} shows the
differences in MRT elements of RIPE's Remote Route Collectors (RRCs) at
the same particular time. The percentage of invalid updates is virtually
equal among all RRCs.

\begin{table}
  \caption{MRT Records, 2017-07-01T00:00+00:00}
  \label{tab:rrc}
  \begin{tabular}{c|rrr|r|c}
  \toprule
  RRC&Valid&Invalid&Not in&Total&Inv.\\&&&RPKI&&in \%\\
  \midrule
  rrc00&\num{835187}&\num{68459}&\num{948935}&\num{10393481}&0.66\\
  rrc01&\num{411349}&\num{33163}&\num{4614574}&\num{5059086}&0.66\\
  rrc02&\multicolumn{4}{c|}{-- collector not used anymore --}&\\
  rrc03&\num{495853}&\num{39312}&\num{5515779}&\num{6050944}&0.65\\
  rrc04&\num{430055}&\num{37239}&\num{4894238}&\num{5361532}&0.69\\
  rrc05&\num{238962}&\num{19692}&\num{2679983}&\num{2938637}&0.67\\
  rrc06&\num{110778}&\num{9111}&\num{1268951}&\num{1388840}&0.66\\
  rrc07&\num{290481}&\num{23758}&\num{3280778}&\num{3595017}&0.66\\
  rrc08&\multicolumn{4}{c|}{-- collector not used anymore --}&\\
  rrc09&\multicolumn{4}{c|}{-- collector not used anymore --}&\\
  rrc10&\num{515789}&\num{42248}&\num{5910603}&\num{6468640}&0.65\\
  rrc11&\num{499675}&\num{41722}&\num{5742000}&\num{6283397}&0.66\\
  rrc12&\num{654993}&\num{54093}&\num{7258880}&\num{7967966}&0.68\\
  rrc13&\num{533517}&\num{45437}&\num{6106805}&\num{6685759}&0.68\\
  rrc14&\num{397131}&\num{32530}&\num{4537170}&\num{4966831}&0.65\\
  rrc15&\num{768287}&\num{62699}&\num{9111875}&\num{9942861}&0.63\\
  rrc16&\num{122493}&\num{9991}&\num{1406753}&\num{1539237}&0.65\\
  rrc17&\multicolumn{4}{c|}{-- no information available --}&\\
  rrc18&\num{105533}&\num{9266}&\num{1213851}&\num{1328650}&0.70\\
  rrc19&\num{364304}&\num{29661}&\num{4196387}&\num{4590352}&0.65\\
  rrc20&\num{1053645}&\num{86577}&\num{12017313}&\num{13157535}&0.66\\
  rrc21&\num{996652}&\num{80354}&\num{11266889}&\num{12343895}&0.65\\
  \bottomrule
  \end{tabular}
\end{table}

When analyzing historical data, a slight increase of valid records (i.e.
RPKI usage) can be noted in table~\ref{tab:hist}, although it's a
subject to reservations since AS numbers and prefixes can be revoked or
re-registered over time. Therefore, the real growth should be higher.

\begin{table}
  \caption{Temporal Development of RPKI Usage with RRC00 RIBs}
  \label{tab:hist}
  \begin{tabular}{c|rr|c}
  \toprule
  Date&Valid&Total&Valid in \%\\
  \midrule
  2012-01-01&\num{421480}&\num{6963682}&6.1\\
  2012-07-01&\num{503910}&\num{7886356}&6.4\\
  2013-01-01&\num{575155}&\num{8851617}&6.5\\
  2013-07-01&\num{600118}&\num{8804669}&6.8\\
  2014-01-01&\num{612287}&\num{8729153}&7.0\\
  2014-07-01&\num{525832}&\num{7147361}&7.4\\
  2015-01-01&\num{610066}&\num{7832287}&7.8\\
  2015-07-01&\num{667992}&\num{8593325}&7.8\\
  2016-01-01&\num{597405}&\num{7615228}&7.8\\
  2016-07-01&\num{652962}&\num{8273659}&7.9\\
  2017-01-01&\num{736358}&\num{9348547}&7.9\\
  2017-07-01&\num{835187}&\num{10393481}&8.0\\
  \bottomrule
  \end{tabular}
\end{table}

